NumPy---Array Programming in Python

### 2020-01-16 body.tex
Avoid repetition
Minor edit

Today, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2019scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It consists of an $n$-dimensional array object along with array-aware functions
that operate on it.
Because of its inherent simplicity---being a pointer to memory with some
associated meta-data---the NumPy array is
the {\it de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
{\it Application Programming Interface} (API) has become ubiquitous as
a language for array programming.

@@

{\em Strides} are necessary to interpret computer memory, which stores elements
linearly, as $n$-dimensional arrays.
It describes the number of bytes to move forward in memory to jump from row to
row, column to column, and so forth.
Consider, for example, a 2-D array of floating point numbers with shape
$(4, 3)$, where each element occupies 8 bytes in memory.
To move between consecutive columns we need to jump forward 8 bytes in memory,
and to access the next row $3 \times 8 = 24$ bytes.
The strides of that array are therefore $(24, 8)$.  NumPy is able to
store arrays in both so-called ``C'' and ``Fortran''-order, iterating
first over either rows or columns.  This allows external libraries
written in those languages to directly access NumPy array data in memory.

>>>>

Today, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2019scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It consists of an $n$-dimensional array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the {\it de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
{\it Application Programming Interface} (API) has become ubiquitous as
a language for array programming.

@@

{\em Strides} are necessary to interpret computer memory, which stores elements
linearly, as $n$-dimensional arrays.
It describes the number of bytes to move forward in memory to jump from row to
row, column to column, and so forth.
Consider, for example, a 2-D array of floating point numbers with shape
$(4, 3)$, where each element occupies 8 bytes in memory.
To move between consecutive columns we need to jump forward 8 bytes in memory,
and to access the next row $3 \times 8 = 24$ bytes.
The strides of that array are therefore $(24, 8)$.  NumPy is able to
store arrays in either C or Fortran memory order, iterating
first over either rows or columns.  This allows external libraries
written in those languages to directly access NumPy array data in memory.
